EGGs are adhesive!

### 2025-03-10 calco/main.tex
strazio di conti

\documentclass[a4paper,UKenglish,cleveref,pdftex,thm-restate,numberwithinsect]{lipics-v2021}
\usepackage{stmaryrd}
\usepackage{bbding}
%\Envelope
\newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}
\usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont}
\usepackage{tikz-cd}
\usepackage{hyperref, cleveref} %simboli matematici
\usepackage[all, cmtip]{xy}

@@

\begin{restatable}{proposition}{regmono}\label{prop:regmono}
	Let $\X$ be an $\mathcal{M}$-adhesive categoru. Then it holds
	\begin{enumerate}
		\item every $\mathcal{M}$-pushout square is also a pullback;
		\item every arrow in $\mathcal{M}$ is a regular mono.
	\end{enumerate}
\end{restatable}
%  [Proof in \Cref{regmono-proof}]

@@

\todo{Inserire bla bla}

%\todo{'sta cragna che segue è falsa come una moneta da 3 euro: cancellare}
%\noindent
%\parbox{7.5cm}{
%	\begin{restatable}{proposition}{mps}\label{prop:kerset}
%		Suppose that in $\Set$ the cube aside is given, whose top and bottom faces are pushout and such that $m\colon A\mto C$, $m'\colon A'\mto C'$ and $g\colon C\mto D$ are injections. Then the right square, made by the kernel pairs of the vertical arrows, is a pushout.
%\end{restatable}}\hfill 
%\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }}

@@

\begin{proposition}\label[proposition]{term:left}The forgetful functor $U_{\tg}$ has a left adjoint $\Delta_{\tg}$.
\end{proposition}
\begin{proof}
	This follows noticing that $\Delta_{\Sigma}(X)$ is a term graph for every object $X$.
\end{proof}

We can list some categorical properties of $\tg$

@@

\begin{restatable}{corollary}{mn}\label{cor:mono2}
	An arrow $(h_E, h_V, h_Q): \mathcal{G\to H}$ in $\EqHyp$ is a regular mono if and only if all its components are injective functions.
\end{restatable}

\iffalse 
\begin{proposition}
	Let $h = (h_E, h_V, h_C): \mathcal{G \to H}$ be a regular mono in $\EqHyp$.
	Then, $h_E$ and $h_V$ are monos and $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{H}\circ h_V$ if and only if $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{G}$.
\end{proposition}

\begin{proof}
	By \Cref{cor:mono2}, we have that $h_E, h_V$ and $h_C$ are all monos.
	Hence, by \Cref{cor:kermono}, $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{G}$ if and only if it is the kernel pair also of $h_C \circ q_\mathcal{G}$, since $h_C$ is mono by hypothesis.
	The thesis follows from $h_C \circ q_\mathcal{G} = q_H \circ h_V$, and from the hypothesis of $h_E$ mono.
\end{proof}

\begin{remark}
	It is possible to restate the last proposition, by \Cref{ex:kernel_pairs_in_Set}, as 
	\begin{displayquote}
		\textit{$h_E$ and $h_V$ are mono and, for every $v, v'\in V_H$, $q_H(h_V(v))=q_H(h_V(v'))$ if and only if $q_G(v)=q_G(v')$}
	\end{displayquote}
	That is, a regular mono in $\EqHyp$ is a morphism that both reflects and preserves equivalences.
	% besides preserving them.
\end{remark}
\fi

@@

We have now all the ingredient necessary to study the adhesivity properties of $\EqHyp$. In particular, we are now going to show that $\EqHyp$ is $\reg(\EqHyp)$-adhesive.

@@

These two property together yields the following fact.

@@

\commentato{
\noindent
\parbox{7.5cm}{
\mps*}
\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }}

\begin{proof}
		Let $E'\subseteq C'$ be the complement of the image of $m'$ and $\iota\colon E'\mto B'$ be the corresponding inclusion. By \Cref{lem:po_set} we know that $(D', \{n', g'\circ \iota\})$ is a coproduct. Thus by \Cref{lem:nodim} we also know that there exists $K_0$, $K_1$, $K_2$ and $K_3$ fitting in the following four pullback diagrams and such that $\{K_d, \{j_i\}_{i=0}^3\}$ is a coproduct.
	\[\xymatrix@C=45pt{K_0 \ar@{>->}[r]^{j_0}  \ar[d]_{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
		B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota)} & D'\times D'}\]
	\[ \xymatrix@C=45pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
		E'\times B' \ar@{>->}[r]_-{(g'\circ \iota) \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota)\times (g'\circ \iota)} & D'\times D'}\]

	Now, if we compute we get
	\begin{align*}
		n\circ b\circ p_0&= d\circ n'\circ p_0= d\circ \pi^1_d\circ j_0=d\circ \pi^2_d\circ j_0=d\circ n'\circ q_0=n\circ b\circ q_0\\
g\circ c \circ  \iota \circ p_3&=d\circ g' \circ  \iota p_3=d\circ \pi^1_d\circ j_3=d\circ \pi^2_d\circ j_3=d\circ g'\circ \iota \circ q_3= g \circ c\circ \iota\circ q_3
	\end{align*}
	Thus, since $n$ and $g$ are mono we get the dotted arrows in the diagram below.
\[\xymatrix{K_0 \ar@/^.3cm/[drr]^{p_0} \ar@{.>}[dr]^{\phi_0} \ar@/_.3cm/[ddr]_{q_0} &&& K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota} \\ &K_b \ar[r]^{\pi^1_d} \ar[d]_{\pi^2_d}& B' \ar[d]^{b} & E' \ar[dr]_{\iota}&K_c \ar[r]^{\pi^1_d} \ar[d]_{\pi^2_d} & C'  \ar[d]^{c}\\ & B' \ar[r]_{b} & B && C' \ar[r]_{c} & C }\]

	Now, we also know that $(C', \{m', \iota\})$ is a coproduct, thus we can apply again \Cref{lem:nodim} to $K_c$ to conclude that $(K_c, \{k_i\}_{i=0}^4)$ is a coproduct, where $k_i\colon K^i_c\to K_c$ is defined by the following pullbacks.

	\[\xymatrix@C=45pt{K_0 \ar@{>->}[r]^{j_0}  \ar[d]_{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
		B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota)} & D'\times D'}\]
	\[ \xymatrix@C=45pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
		E'\times B' \ar@{>->}[r]_-{(g'\circ \iota) \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota)\times (g'\circ \iota)} & D'\times D'}\]

	Let $u\colon K_b\to Z$ and $v\colon K_c\to Z$ be two arrows such that $u\circ k_{f'}=v\circ k_{m'}$. We want to construct an arrow $w\colon K_d\to Z$ such that $w\circ k_{g'}=v$ and $w\circ k_{n'}=u$.
\end{proof}
}

>>>>

\documentclass[a4paper,UKenglish,cleveref,pdftex,thm-restate,numberwithinsect]{lipics-v2021}
\usepackage{stmaryrd}
\usepackage{bbding}
%\Envelope
\newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}

\newcommand{\pbc}{\mathsf{Pb}}
\usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont}
\usepackage{tikz-cd}
\usepackage{hyperref, cleveref} %simboli matematici
\usepackage[all, cmtip]{xy}

@@

\begin{restatable}{proposition}{regmono}\label{prop:regmono}
	Let $\X$ be an $\mathcal{M}$-adhesive category. Then it holds
	\begin{enumerate}
		\item every $\mathcal{M}$-pushout square is also a pullback;
		\item every arrow in $\mathcal{M}$ is a regular mono.
	\end{enumerate}
\end{restatable}
%  [Proof in \Cref{regmono-proof}]

@@

Focusing on $\Set$, we can prove a sharper result (see \Cref{proof:kerset} for the proof).

\noindent
\parbox{7.5cm}{\begin{restatable}{lemma}{mps}\label{prop:kerset}
	Suppose that in $\Set$ the cube in the diagram on the left is given, whose top and bottom faces are pushout, the left face a pulllback and such that $m\colon A\mto C$ is an injection. Then the following are true:
	\parbox{14cm}{\begin{enumerate}
		\item the right face of the cube is a pullback too;
		\item the right square, made by the kernel pairs of the vertical arrows, is a pushout.
	\end{enumerate}}
\end{restatable}}\hfill 
\parbox{6cm}{\vspace{-1.1cm}\xymatrix@C=10pt@R=5pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }}

@@

\begin{proposition}\label[proposition]{term:left}The forgetful functor $U_{\tg}$ has a left adjoint $\Delta_{\tg}$.
\end{proposition}
\commentato{
\begin{proof}
	This follows noticing that $\Delta_{\Sigma}(X)$ is a term graph for every object $X$.
\end{proof}}

We can list some other categorical properties of $\tg$.

@@

\begin{restatable}{corollary}{mn}\label{cor:mono2}
	An arrow $(h_E, h_V, h_Q): \mathcal{G\to H}$ in $\EqHyp$ is a regular mono if and only if all its components are injective functions.
\end{restatable}\todo{manca ancora la dimostrazione dell'implicazione da destra a sinistra}

@@

We have now all the ingredient necessary to study the adhesivity properties of $\EqHyp$.  As a first step we need to introduce a class $\mathcal{M}$ of monos.

\begin{definition}
	contenuto...
\end{definition}

\begin{restatable}{lemma}{pbm}\label{lem:pbmono}
	The class $\pbc$ is closed under composition, decomposition and it is stable under pullbacks and pushouts
\end{restatable}

In particular, we are now going to show that $\EqHyp$ is $\reg(\EqHyp)$-adhesive.

@@

\noindent
\parbox{11cm}{
\begin{remark}\label{rem:disj}
	Notice that extensivity entails that coproducts are \emph{disjoint}, i.e.~ that the pullback between two coproduct injections is given by the initial object (with initial maps ad coprojections). To see this, let $\{X, \{j_i\}_{i\in I}\}$ be the coproduct of the family $\{X_i\}_{i\in I}$ and let $k$ be an element of $I$. Then  $(X_k, \{t_i\}_{i\in I})$ with
	\[t_i=\begin{cases}
		\id{X_k} & i=k\\?_{X_k} & i\neq k
	\end{cases}\]
	is a coproduct and so the squares on the right are pullbacks.
\end{remark}}\hfill\parbox{2cm}{\vspace{-1.5cm}\xymatrix@R=15pt{\emptyset \ar@{>->}[d]_{?_{X_i}} \ar@{>->}[r]_{?_{X_k}}& X_k \ar@{>->}[d]^{j_k} \\ X_i \ar@{>->}[r]^{j_i} & X} \xymatrix@R=15pt{X_k \ar[r]_{\id{X}} \ar[d]_{\id{X}}& X_k \ar@{>->}[d]^{j_k}\\X_k \ar@{>->}[r]^{j_k} & X}}

In particular, the previous remark yields at once the following fact.

\noindent 
\parbox{11.5cm}{\begin{proposition}\label{prop:isempty}
	Suppose that the square on the right is a pullback. Let $\iota \colon E\mto Y$ be the inclusion of the complement of the image of $p_1$. If there exist two  arrows $t_1\colon T\to E$ and $t_2\colon T\to X$ such that \[g\circ \iota\circ t_1= f\circ t_2\] then $T$ is empty.
\end{proposition}}\hfill \parbox{2cm}{\vspace{-1.5cm}\xymatrix@R=15pt{P \ar[r]_{p_1} \ar[d]_{p_2}& Y \ar[d]^{g}\\X \ar[r]^{f}& Z}}
\begin{proof}
	By the universal property of pullbacks we get an arrow $t\colon T\to P$ such that 
	\[p_1\circ t=\iota \circ t_1 \qquad p_2\circ t=t_2\]
	\parbox{2cm}{\xymatrix{T \ar@{.>}[r]^{s}\ar@{>>}[dr]_{\pi} \ar@/^.4cm/[rr]^{t_1} & \emptyset \ar@{>->}[r]_{?_{E}} \ar@{>->}[d]_{?_I}& E \ar@{>->}[d]^{\iota}\\ & I \ar@{>->}[r]_{i} & Y}}\hfill \parbox{10.5cm}{Let $i\colon I\mto Y$ be the inclusion of the image of $p_1$, so that we have also an epi $q\colon P\eto I$. By definition of complement $(Y, \{i, \iota\})$ is a coproduct, thus by  \Cref{rem:disj} the inner square in the diagram on the left is a pullback and we get a dotted arrow $s\colon T\to \emptyset$ filling the diagram. But a set with an arrow towards the empty set must be empty and we conclude. \qedhere }
\end{proof}

Extensivity and distributivity, moreover, yield the following fact.

@@

We are now ready to exploit the previous propertis to prove \Cref{prop:kerset}, as promised.

\noindent
\parbox{7.5cm}{\mps*}\hfill
\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{->}[rr]_{g} & & D }}

\begin{proof}\label{proof:kerset}
	We can start noticing that $m'$, being the pullback of $m$ is mono too. This, in turn, entails that $n$ and $n'$ are mono too because in $\Set$, as in any adhesive category, monomorphisms are stable under pushouts.

	\noindent 
	\parbox{11.5cm}{\hspace{15pt}
	Let $\iota' \colon E'\mto C'$ and $\iota\colon E\to C$ be the inclusions of the complement of the images of of $m'$ and $m$ respectively . By \Cref{lem:po_set}, $(D', \{n', g'\circ \iota\})$ and $(D, \{n, g\circ \iota\})$ are coproducts. We can also notice that $c\circ \iota'$ factors through $E$, as shown by the square on the right.}\hfill \parbox{4cm}{\vspace{-5pt}\xymatrix@R=15pt{E' \ar@{.>}[d]_{w} \ar@{>->}[r]_{\iota'} & C' \ar[d]^{c}\\ E \ar@{>->}[r]_{\iota} & C}}

	\noindent
	\parbox{10.5cm}{\hspace{15pt}To see this, let $e$ be in $E'$ and suppose that  $c(\iota'(e))=m(x)$ for some $x\in A$. Then we can apply the  universal property of pullbacks to build the dotted arrow in the diagram aside, where $v_0$ and $v_1$ are the arrows picking $x$ and $\iota'(e)$, respectively. But then $e$ must belong to the image of $m'$, which is a contradiction.}\hfill  \parbox{4cm}{\xymatrix@R=15pt{1 \ar[dr]_{v_0}  \ar@/^.3cm/[rr]^{v_1} \ar@{.>}[r]_{v}& A' \ar[d]_{a} \ar@{>->}[r]_{m'} & C' \ar[d]^{c}\\& A  \ar@{>->}[r]^{m}& C}}

	\begin{enumerate}
		\item Consider two arrows $t_1\colon T\to D' $ and $t_2\colon T\to B$ such that $d\circ t_1=n\circ t_2$. By extensivity

		\noindent\parbox{9.5cm}{ of $\Set$, we already know that $(T, \{l_i\}_{i=0}^1)$ is a coproduct, where $l_i\colon T_i\mto T$ are defined by the diagram aside, whose two halves are pullbacks aside. }\hfill\parbox{4cm}{\xymatrix@R=15pt{T_0 \ar@{>->}[r]_{l_0} \ar[d]_{h_0} & T \ar[d]^{t_1} & T_1 \ar@{>->}[l]^{l_1} \ar[d]^{h_1}\\ E' \ar@{>->}[r]^{g'\circ \iota'} & D' & B' \ar@{>->}[l]_{n'}}}

		If we compute we get
		\[g\circ c \circ \iota' \circ h_0=d\circ g'\circ \iota' \circ h_0=d\circ t_1\circ l_0=n\circ t_2\circ l_0\]

		By adhesivity of $\Set$ and \Cref{prop:regmono} the bottom face of the given cube is a pullback, therefore there exists an arrow $u\colon T_0\to A$ such that 
		\[f\circ u=b\circ t_2\circ l_0 \qquad m\circ u=c\circ \iota'\circ h_0\]

	By \Cref{prop:isempty} we conclude that $T_0$ is empty. Therefore $l_1$ is an isomorphism and we have $n'\circ h_1\circ l^{-1}_1=t_1$. On the other hand
\[n\circ b\circ h_1\circ l^{-1}_1=d\circ n'\circ h_1\circ l^{-1}_1=d\circ t_1=n\circ t_2\]
And we can conclude that $b\circ \circ h_1\circ l^{-1}_1=t_2$ because $n$ is a mono. The thesis now follows from the fact that  also $n'$ is mono.

		\item  By \Cref{lem:nodim} we know that there exists $K_0$, $K_1$, $K_2$ and $K_3$ fitting in the following four pullback diagrams and such that $\{K_d, \{j_i\}_{i=0}^3\}$ is a coproduct.
		\[\xymatrix@C=45pt{K_0 \ar@{>->}[r]^{j_0}  \ar[d]_{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
			B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota')} & D'\times D'}\]
		\[ \xymatrix@C=45pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
			E'\times B' \ar@{>->}[r]_-{(g'\circ \iota') \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota')\times (g'\circ \iota')} & D'\times D'}\]

	Now, if we compute we get
\begin{align*}
	n\circ b\circ p_0&= d\circ n'\circ p_0= d\circ \pi^1_d\circ j_0=d\circ \pi^2_d\circ j_0=d\circ n'\circ q_0=n\circ b\circ q_0\\
	g\circ c \circ  \iota' \circ p_3&=d\circ g' \circ  \iota' p_3=d\circ \pi^1_d\circ j_3=d\circ \pi^2_d\circ j_3=d\circ g'\circ \iota' \circ q_3= g \circ c\circ \iota'\circ q_3
\end{align*}
Thus, since $n$ and $g$ are mono we get the dotted arrows in the diagram below.
\[\xymatrix{K_0 \ar@/^.3cm/[drr]^{p_0} \ar@{.>}[dr]^{\phi_0} \ar@/_.3cm/[ddr]_{q_0} &&& K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota'} \\ &K_b \ar[r]^{\pi^1_b} \ar[d]_{\pi^2_b}& B' \ar[d]^{b} & E' \ar[dr]_{\iota'}&K_c \ar[r]^{\pi^1_c} \ar[d]_{\pi^2_c} & C'  \ar[d]^{c}\\ & B' \ar[r]_{b} & B && C' \ar[r]_{c} & C }\]

Notice, moreover, that 
\[(\pi^1_d, \pi^2_d)\circ k_{g'}\circ \phi_3=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ \phi_3=(g'\times g')\circ (\iota'\circ p_3, \iota'\circ q_3)\]
and so $k_{g'}\circ \phi_3=j_3$.

Now, we also have
\begin{align*}
	n\circ b\circ p_1&=d\circ n'\circ p_1=d\circ \pi^1_d\circ j_1=d\circ \pi^2_d\circ j_1=d\circ g'\circ \iota'\circ q_1\\
	n\circ b\circ q_2 &=d\circ n'\circ p_2=d\circ\pi^2_D\circ j_2
	=d\circ \pi^1_d\circ j_2=d\circ g'\circ \iota'\circ p_2
\end{align*}

			Since the bottom face of the original cube is a pullback (again by \Cref{prop:regmono}), we conclude that there exist arrows $k_1\colon  K_1\to A$ and $k_2\colon K_2\to A$ such that
			\[m\circ k_1=\iota'\circ q_1 \quad f\circ k_1=b\circ p_1 \quad m\circ k_2=\iota'\circ q_2 \quad f\circ k_2=b\circ q_2\]

			By \Cref{prop:isempty} we conclude that $K_1$ and $K_2$
 are both empty. In particular, we can also deduce that $(K_d, \{j_0, j_3\})$ is a coproduct.

 	\smallskip
 \parbox{7.5cm}{We can go further. The outer part of the diagram on the right commutes, so that we have the dotted $\psi_0\circ K_b\to K_0$.
 Now, on the one hand $\phi_0\circ \psi_0=\id{K_b}$ because if we compute we get:
  \[(\pi^1_b, \pi^2_b)\circ \phi_0\circ \psi_0=(p_0, q_0)\circ \psi_0=(\pi^1_b, \pi^2_b)\]}\hfill \parbox{4cm}{\vspace{-.5cm}\xymatrix{K_b \ar[dr]_{(\pi^1_b, \pi^2_b)}  \ar@{>->}@/^.4cm/[rr]^{k_{n'}} \ar@{.>}[r]_{\psi_0}& K_0 \ar@{>->}[r]_{j_0}  \ar[d]^{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)} \\
 	& B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' }
 	}

 On the other hand, notice that 
 \[\pi^1_{d}\circ k_{n'}\circ \phi_0=n'\circ \pi^1_b\circ \phi_0=n'\circ p_0=\pi^1_d\circ j_0 \qquad \pi^2_{d}\circ k_{n'}\circ \phi_0=n'\circ \pi^2_b\circ \phi_0=n'\circ p_0=\pi^2_d\circ j_0\]

 Thus $k_{n'}\circ \phi_0=j_0$ and we have
 \[(p_0, q_0)\circ \psi_0\circ \phi_0=(\pi^1_b, \pi^2_b)\circ \phi_0=(p_0, q_0)= \quad  j_0\circ \psi_0\circ \phi_0 = k_{n'}\circ \phi_0=j_0\]
We can conclude that $\phi_0$ is an isomorphism and that $k_{n'}$ is a coproduct injection.

 Furthermore, by definition of complement, $(C', \{\iota', m'\})$ is a coproduct. Applying again \Cref{lem:nodim} we can decompose $K_c$ in four parts, given by the pullbacks below:
 \[\xymatrix@C=45pt{H_0 \ar@{>->}[r]^{x_0}  \ar[d]_{(y_0, z_0)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_1 \ar@{>->}[r]^{x_1}  \ar[d]_{(y_1, z_1)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
 	A'\times A' \ar@{>->}[r]_-{m'\times m'} & C'\times C' & A'\times E' \ar@{>->}[r]_-{m'\times  \iota'} & C'\times C'}\]
 \[ \xymatrix@C=45pt{H_2 \ar@{>->}[r]^{x_2}  \ar[d]_{(y_2, z_2)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_3 \ar@{>->}[r]^{x_3}  \ar[d]_{(y_3, z_3)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
 	E'\times A' \ar@{>->}[r]_-{\iota' \times m'} & C'\times C' & E'\times E' \ar@{>->}[r]_-{ \iota'\times  \iota'} & C'\times C'}\]

 Now, notice that
 \small
 \[\begin{split}
(\pi^1_d, \pi^2_d)\circ k_{g'}\circ x_1&=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ x_1\\=&(g'\times g')\circ (m'\times \iota')\circ (y_1, z_1)\\=&((g'\circ m') \times (g'\circ \iota'))\circ (y_1, z_1)\\=&((n'\circ f') \times (g'\circ \iota'))\circ (y_1, z_1)\\=&(n'\times  (g'\circ \iota'))\circ (f'\circ y_1, z_1)
 \end{split} \hspace{1pt} \begin{split}
 (\pi^1_d, \pi^2_d)\circ k_{g'}\circ x_2&=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ x_2\\=&(g'\times g')\circ ( \iota' \times m')\circ (y_2, z_2)\\=&((g'\circ \iota') \times (g'\circ m'))\circ (y_2, z_2)\\=&( (g'\circ \iota') \times (n'\circ f'))\circ (y_2, z_2)\\=&((g'\circ \iota') \times n')\circ (y_2, f'\circ z_2)
 \end{split} \]
\normalsize
 thus we have arrows $h_1\colon H_1\to K_1$ and $h_2\colon H_2\to K_2$, showing that $H_1$ and $H_2$ are empty. On the other hand, let us consider the two diagrams below.

 \[ \xymatrix@C=45pt{ H_3 \ar@{.>}[d]^{\alpha_3} \ar[r]^{x_3} \ar@/_.4cm/[dd]_{(y_3, z_3)} & K_c \ar[d]_{k_{g'}}& K_3 \ar@{.>}[d]^{\beta_3} \ar@/^.3cm$ $/[dr]^{\phi_3} \ar@/_.4cm/[dd]_{(p_3, q_3)}\\K_3 \ar@{>->}[r]^{j_3}  \ar[d]^{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} &  H_3 \ar@{>->}[r]^{x_3}  \ar[d]^{(y_3, z_3)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)}  \\
   E'\times E' \ar@{>->}[r]_-{(g'\circ \iota')\times (g'\circ \iota')} & D'\times D' & E'\times E' \ar@{>->}[r]_-{ \iota'\times  \iota'} & C'\times C'}\]
 Their solid part commute, indeed we have:
 \[\begin{split}
 	(\pi^1_d, \pi^2_d\circ k_{g'})\circ x_3&=(g'\times g')\circ (\pi^1_c, \pi^2_c) \circ x_3\\=&(g'\times g')\circ (\iota'\times \iota')\circ (y_3\times z_3)\\=&(g'\circ \iota') \times (g'\circ \iota')\circ (y_3, z_3)
 \end{split}\qquad \begin{split}
 (\pi^1_c, \pi^2_c)\circ \phi_3=&(\iota'\circ p_3, \iota' \circ q_3)\\=&
(\iota'\times \iota')\circ (p_3, q_3)\\& \end{split}\]

Thus we get the dotted arrows $\alpha_3$ and $\beta_3$. Now, they are one the inverse of the other. Indeed on the one hand we have:
\begin{align*}
j_3\circ \alpha_3\circ \beta_3&=k_{g'}\circ x_3\circ \beta_3=k_{g'} \circ \phi_3=\phi_3 \\
(p_3, q_3)\circ \alpha_3\circ \beta_3&=(y_3, z_3)\circ \beta_3=(p_3, q_3) 
\end{align*}
 On the other, notice that
 \[(\pi^1_c, \pi^2_c)\circ \phi_3\circ \alpha_3 =(\iota'\times \iota')\circ (p_3, q_3)\circ \alpha_3= (\iota'\times \iota')\circ (y_3, z_3)=(\pi^1_c, \pi^2_c)\circ x_3\]
 Therefore $\phi_3\circ \alpha_3=x_3$ and thus $x_3\circ \beta_3\circ \alpha_3=x_3$. Moreover:
 \[(y_3, z_3)\circ \beta_3\circ \alpha_3=(p_3, q_3\circ \alpha_3)=(y_3, z_3)\]

 Summing up, we have just proved that $(K_c, \{x_0, \phi_3\})$ is a coproduct.

 Let now $\gamma\colon K_b\to Z$ and $\delta\colon K_c\to Z$ be two arrows such that $\gamma\circ k_{f'}=\delta\circ k_{m'}$. We want to construct an arrow $\theta\colon K_d\to Z$ such that $\theta\circ k_{g'}=\delta$ and $\theta\circ k_{n'}=\gamma$.

 Now, we have already proved that $(K_d, \{k'_n, j_3\})$ is a coproduct, thus there is a unique arrow $\theta\colon K_d\to Z$ such that 
 \[\theta \circ k'_n=\gamma \qquad \theta \circ j_3=\delta \circ \phi_3 \]
 Now, on the one hand we have
 \begin{align*}
 	\theta \circ k_{g'}\circ \phi_3=\theta \circ  j_3=\delta\circ \phi_3 
 \end{align*}

 On the other hand, 
 \[(\pi^1_d, \pi^2_d)\circ k_{g'}\circ x_0=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ x_0=(g'\times g')\times (m'\times m')\circ (y_0, x_0)=(n'\circ n')\ (f')\]

			 \qedhere 
	\end{enumerate}
\end{proof}
